### 2017-02-26 2017mergingmerges/section/XX-Processes.tex
Fold in written notes

Overall, our fusion algorithm has taken two separate processes that we once imagined to be running concurrently, and has produced a single sequental result process that implements both. We have chosen a \emph{specific sequential order} in which to interleave instructions that implement both original processes. As with the Flow Fusion system of \citet{lippmeier2013data} we have performed the job of a concurrent scheduler at compile time. However, in contrast to Flow Fusion and similar systems, we do not need to organize statements into a fixed \emph{loop anatomy}, we simply merge them as they are. This allows us to implement a wider range of processes, including ones with nested loops that work on segmented streams, which we discuss further in \S\ref{s:FutureWork}.

@@

\newcommand\annot[5]{
  \tiny ((#1,   \> \tiny \{sIn1 =      #2\}), 
                \> \tiny (#3, \> \tiny \{sIn1 =      #4, \> \tiny sIn2 =      #5\}))
}
\newcommand\icase[7]{
 \tt{#1} \> \tt{= #2} \> \tt{#3} \{\tt{#4}\} \> \tt{#5} \{\tt{#6}\} \> \tiny #1 \> \tiny = #7 \\
}
\newcommand\instr[5]{
 \tt{#1}\>\tt{= #2} \> \tt{#3} \{\tt{#4}\} \> \> \tiny #1 \> \tiny = #5 \\
}
\begin{tabbing}
@  @ \=
@, F17@  \= = @case (f || (l /= v)) @
         \= @F17{}         @ \= @F17{ }@
@   @ \= \tiny F17 \= \tiny = ((A0, \= \tiny \{sIn1 = pending\}), \= \tiny (B0, \= \tiny \{sIn1 = pending, \= \tiny sIn2 = pending\})) \kill
\> @{@ \instr{F0}{pull sIn1 b1}{F1}{}
      {\annot{A0}{none}{B0}{none}{none}}

>>>>

Overall, our fusion algorithm has taken two separate processes that we once imagined to be running concurrently, and has produced a single sequental result process that implements both. We have chosen a \emph{specific sequential order} in which to interleave instructions that implement both original processes. As with the Flow Fusion system of \cite{lippmeier2013data} we have performed the job of a concurrent scheduler at compile time. However, in contrast to Flow Fusion and similar systems, we do not need to organize statements into a fixed \emph{loop anatomy}, we simply merge them as they are. This allows us to implement a wider range of processes, including ones with nested loops that work on segmented streams, which we discuss further in \S\ref{s:FutureWork}.

@@

\newcommand\annot[5]{
  \tiny ((#1,   \> \tiny \{sIn1 =      #2\}), 
                \> \tiny (#3, \> \tiny \{sIn1 =      #4, \> \tiny sIn2 =      #5\}))
}
\newcommand\icase[7]{
 \tt{#1} \> \tt{= #2} \> \tt{#3} \{\tt{#4}\} \> \tt{#5} \{\tt{#6}\} \> \tiny #1 \> \tiny = #7 \\
}
\newcommand\instr[5]{
 \tt{#1}\>\tt{= #2} \> \tt{#3} \{\tt{#4}\} \> \> \tiny #1 \> \tiny = #5 \\
}
\begin{tabbing}
@  @ \=
@, F17@  \= = @case (f || (l /= v)) @
         \= @F17{x1 = b1, f = F}@ \= @F17{ }@
@      @ \= \tiny F17 \= \tiny = ((A0, \= \tiny \{s1 = pending\}), \= \tiny (B0, \= \tiny \{s1 = pending, \= \tiny s2 = pending\})) \kill
\> @{@ \instr{F0}{pull sIn1 b1}{F1}{}
      {\annot{A0}{none}{B0}{none}{none}}
